Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-09 paper.tex
finish off open access section

>>>>

Medical journals are not the only source of information that can sit behind a paywall.
Sometimes, as in the previous case, there is information that one might argue is unjustly
kept away from the common man. What one considers to be unjust is subjective, but the idea
is that piracy is a tool that consumers can employ to fight systems that they deem to be
unjust. Without piracy, one might have to roll over and accept their limited access or
resort to a more extreme and likely illegal approach. To put it another way, piracy acts
as a check on businesses to discourage them from integrating unpopular, anti-consumer
practices into their business model. When a consumer wants to purchase something and they
cannot afford it, they might start to look for alternative way of obtaining it. But, when
they can afford it and they think it is fairly priced, they will purchase it. Thus, piracy
is often where tech-savvy persons turn to when they need something that they feel is
exorbitantly priced, but is not often utilized when they feel the purchase is worthwhile.
This way, piracy acts as a safeguard for consumers when they feel they are being taken
advantage of by predatory business practices.
% XXX the statements in the paragraph above are largely unsubstantiated >:D
% XXX add darnton:pirating-and-publishing and bohannon:everyone sources if needed
